Disclosing funding sources for open access publication fees: the Open APC initiative

### 2016-04-07 article.Rmd
minor typo

Publication fees, often paid by funders or universities, are a widely discussed open access business model. Yet, how and to what extent these activities are effective in terms of the number of supported research articles and associated costs remains under debate. This paper describes the Open APC initiative[^2], in which German universities and research organization share spendings on open access publication fees, and how it is currently implemented. More specifically, it addresses three problem areas when studying the economical effects of open access publishing: fragmentation of open access funding, variable pricing schemes and the comparison across research institutions. Such an approach extends methods and improves data collection activities for researchers and practitioners, as well as contribute to a better understanding of factors affecting the analysis of publication fees in open access publishing.

>>>>

Publication fees, often paid by funders or universities, are a widely discussed open access business model. Yet, how and to what extent these activities are effective in terms of the number of supported research articles and associated costs remains under debate. This paper describes the Open APC initiative[^2], in which German universities and research organization share spending on open access publication fees, and how it is currently implemented. More specifically, it addresses three problem areas when studying the economical effects of open access publishing: fragmentation of open access funding, variable pricing schemes and the comparison across research institutions. Such an approach extends methods and improves data collection activities for researchers and practitioners, as well as contribute to a better understanding of factors affecting the analysis of publication fees in open access publishing.
